---
title: "MATH4753 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753stee0082Sp25)
```


# Introduction

This is my R package for MATH 4753

## FIREDAM
```{r}
data("FIREDAM")
```
Fire Damage Data

## mybin
```{r}
MATH4753stee0082Sp25::mybin(iter=10000,n=15, p=0.3)
```
My Binomial Function

## myboot2
```{r}
MATH4753stee0082Sp25::myboot2(x=rnorm(20,mean=10,sd=5),xlab="std deviation",fun="sd",col="lightblue")
```
Bootstrap estimation


## mycltu
```{r}
MATH4753stee0082Sp25::mycltu(n=5,iter=20000,a=1,b=7)
```
A function showing an application of the central limit theorem on a uniformly distributed random variable

## mymaxlik
```{r}
MATH4753stee0082Sp25::mymaxlik(c(3,3,4,3,4,5,5,4),param=seq(0,1,length=10001),lfun=function(x,param){log(dbinom(x,prob=param,size=20))},xlab=expression(pi),main="Binomial",cex.main=2)
```
My max likelihood function


## myncurve
```{r}
MATH4753stee0082Sp25::myncurve(5.5, 2.3, 6)
```
My Normal Curve Function


## mysq
```{r}
MATH4753stee0082Sp25::mysq(1:10)
```
Mysquared Function


## ntickets
```{r}
MATH4753stee0082Sp25::ntickets(N=400, gamma=0.02, p=0.95)
```
Uses binomial and normal variables to test the number of tickets an airline should sell given parameters

## scatterhist
```{r}
ddt <- read.csv("CDDT.csv")
with(ddt, MATH4753stee0082Sp25::scatterhist(LENGTH,WEIGHT, xlab="LENGTH"))
```
Scatterplot Histogram
